; This plugin matches entities to articles, so relevant articles unlock as things are discovered.
; Examples of this feature would include talking to specific characters, wearing a faction's armour etc.

; Fills tables with a section's contents.
; Only used by scripts, and has hardcoded references.
; Do not touch this section unless you know what you are doing!
[encyclopedia_interactivity]
characters = encyclopedia_interactivity_characters
items = encyclopedia_interactivity_items
mutants = encyclopedia_interactivity_mutants
smarts = encyclopedia_interactivity_smarts
vehicles = encyclopedia_interactivity_vehicles

; Characters - triggered by looting or talking-to.
[encyclopedia_interactivity_characters]
bar_visitors_barman_stalker_trader = encyclopedia_characters_barkeep
esc_2_12_stalker_nimble = encyclopedia_characters_nimble
esc_m_trader = encyclopedia_characters_sidorovich
zat_a2_stalker_barmen = encyclopedia_characters_beard

; Items - triggered by using or acquiring.
[encyclopedia_interactivity_items]

; Mutants - triggered by field dressing.
[encyclopedia_interactivity_mutants]
bloodsucker = encyclopedia_mutants_bloodsucker
boar = encyclopedia_mutants_boar
burer = encyclopedia_mutants_burer
cat = encyclopedia_mutants_cat
chimera = encyclopedia_mutants_chimera
controller = encyclopedia_mutants_controller
crow = encyclopedia_mutants_crow
dog = encyclopedia_mutants_blind_dog
flesh = encyclopedia_mutants_flesh
fracture = encyclopedia_mutants_fracture
gigant = encyclopedia_mutants_pseudogiant
karlik = encyclopedia_mutants_karlik
pseudodog = encyclopedia_mutants_pseudodog
psy_dog = encyclopedia_mutants_psydog
rat = encyclopedia_mutants_rat
snork = encyclopedia_mutants_snork
tushkano = encyclopedia_mutants_tushkano
zombie = encyclopedia_mutants_zombie

; Smart terrains - triggered by walking into.
[encyclopedia_interactivity_smarts]

; Vehicles - triggered by entering.
[encyclopedia_interactivity_vehicles]
