; This plugin details the recoil effects of weapons when the enhanced recoil feature is enabled.
; Each weapon should have a section of the same name here, with its name also listed in the "enhanced_recoil" section.

; Speed of camera movement can be altered with the "speed" attribute.
; Values should be "1" for high-RPM MGs, "2" for slow-RPM MGs or heavy weapons, and "3" for shotguns.
; If an invalid number is provided then it will default to whichever is nearest to that given.

; Effects are set separately for when the actor is zoomed in or out of their weapon.
; The attributes for these are "zoom_in_effects" and "zoom_out_effects" respectively.
; Only the first four effects are used, i.e. one for each available animation type.
; Any decimal values are used to help provide randomness to the "strength" of the effect.
; First moves the camera back, second turns left/right, third turns upward, fourth tilts left/right.
; If there are any additional effects which you list after these, they are ignored and will not be used.

; Two additional "global" zoom multipliers exist, but it isn't advised to use them.
; Said multipliers are "zoom_in_multi" and "zoom_out_multi".

; An additional multiplier also exists to strengthen/weaken the effects of recoil reduction via upgrades.
; The higher the "upgrade_multi" value, the more of a dampening effect said upgrades will have (and vice versa).

; On top of all of this another multiplier, "k_cam_dispersion", can be used by ammunition to increase or decrease weapon recoil.
; This means alternate ammo types can be made to kick harder than normal - but without detriment to those who play with this feature disabled.

[enhanced_recoil]
;wpn_ak74
;wpn_mp5

[wpn_ak74]
speed = 2
zoom_in_effects = 1, 1.1, 2, 0.9
zoom_out_effects = 0.5, 0.55, 1, 0.45
upgrade_multi = 1

[wpn_mp5]
speed = 1
zoom_in_effects = 0.4, 0.6, 0.9
zoom_out_effects = 0.2, 0.3, 0.45
upgrade_multi = 1
