; Any NPC can use this feature if given the 'dm_orders_dialog' actor dialog in their character profile
; Simply copy and modify this file as <spawn_section>_orders.ltx

; Potential items which can be received depending on selection.
; Multiple items can be given at once if you separate them with a comma.

; Pistols.
[category_1]
title = st_esc_2_12_stalker_nimble_category_1_title
wait_time = 43200
cost = 6300
item1 = wpn_desert_eagle_nimble
item2 = wpn_sig220_nimble
item3 = wpn_usp_nimble

; Sub-machine guns.
[category_2]
title = st_esc_2_12_stalker_nimble_category_2_title
wait_time = 43200
cost = 16200
item1 = wpn_mp5_nimble
item2 = wpn_spas12_nimble
item3 = wpn_protecta_nimble

; Assault rifles.
[category_3]
title = st_esc_2_12_stalker_nimble_category_3_title
wait_time = 43200
cost = 27000
item1 = wpn_groza_nimble
item2 = wpn_g36_nimble
item3 = wpn_fn2000_nimble

; Sniper rifles.
[category_4]
title = st_esc_2_12_stalker_nimble_category_4_title
wait_time = 64800
cost = 39600
item1 = wpn_vintorez_nimble
item2 = wpn_svu_nimble
item3 = wpn_svd_nimble

; Headgear.
[category_5]
title = st_esc_2_12_stalker_nimble_category_5_title
wait_time = 64800
cost = 45000
item1 = helm_hardhat, cs_heavy_outfit

; Scientific outfits.
[category_6]
title = st_esc_2_12_stalker_nimble_category_6_title
wait_time = 64800
cost = 108000
item1 = scientific_outfit

; Exoskeleton outfits.
[category_7]
title = st_esc_2_12_stalker_nimble_category_7_title
wait_time = 86400
cost = 225000
item1 = exo_outfit

; Special outfits.
[category_8]
title = st_esc_2_12_stalker_nimble_category_8_title
wait_time = 86400
cost = 170000
item1 = commander_outfit